\papertitle

### 2013-02-05 manuscript.tex
more edits in section 3

We initialize the particles 
uniformly across the frame before tracking begins. To improve numerical 
stability, we normalize the weights of all particles on each iteration, and 
only resample the particle population when the mean particle weight falls 
below a pre-determined threshold. 
%............................................................................%
\subsubsection{Motion Model}
Our motion model (Equation~\ref{eq:motion_model}) is a simple Gaussian transition 
centered around each particle's current position, augmented with an 
$\epsilon$-random uniform sampling strategy. The sampling law is as follows:\begin{equation}
\label{eq:motion_model}
x^{[i]}_t \sim \begin{cases}
\mathcal{N}(x^{[i]}_{t-1}, \Sigma), &\text{with probability } 1-\epsilon \\
\mathcal{U}(0,b),& \text{with probability } \epsilon \\
\end{cases}\\
\end{equation}
In Equation~\ref{eq:motion_model}, $x^{[i]}_t$ is the position of the $i^\text{th}$ 
particle in pixel space at time $t$, $\Sigma$ is a chosen covariance matrix, and $b$ 
is a vector of the bounds of the pixel space. The sampling method requires that, with 
probability $\epsilon$, the particle filter will choose a pixel from a uniform 
distribution of all of the pixels in the pixel space for the location of the $i^\text{th}$ 
particle. The $\epsilon$-random uniform transitions increase tracking robustness, by 
forcing the filter to always sample broadly across the pixel space. This helps prevent 
overconfidence and collapse, and decreases reacquisition delay.

>>>>

We initialize the particles 
uniformly across the frame before tracking begins. To improve numerical 
stability, we normalize the weights of all particles on each iteration, and 
only resample the particle population when the mean particle weight falls 
below a pre-determined threshold. 
%............................................................................%
\subsubsection{Motion Model}
Our motion model (Equation~\ref{eq:motion_model}) is a simple Gaussian transition 
centered around each particle's current position, augmented with an 
$\epsilon$-random uniform sampling strategy. The sampling law is as follows:\begin{equation}
\label{eq:motion_model}
x^{[i]}_t \sim \begin{cases}
\mathcal{N}(x^{[i]}_{t-1}, \Sigma), &\text{with probability } 1-\epsilon \\
\mathcal{U}(0,b),& \text{with probability } \epsilon \\
\end{cases}\\
\end{equation}
In Equation~\ref{eq:motion_model}, $x^{[i]}_t$ is the position of the $i^\text{th}$ 
particle in 640x480 pixel space at time $t$, $\Sigma$ is a chosen covariance matrix, and $b$ 
is a vector of the bounds of the pixel space. The sampling method requires that, with 
probability $\epsilon$, the particle filter will choose a pixel from a uniform 
distribution of all of the pixels in the pixel space for the location of the $i^\text{th}$ 
particle. The $\epsilon$-random uniform transitions increase tracking robustness, by 
forcing the filter to always sample broadly across the pixel space. This helps prevent 
overconfidence and collapse, and decreases reacquisition delay.
